### 2018-04-19 concepts.tex
aflfuzz

In scientific literature, the most frequently proposed solution is the
use of replications:  repeated runs of ``successful'' experiments to
minimize the probability that a result is a fluke due to publication
bias.  One way to produce this effect would be to allow
delta-debugging to backtrack if the probabilties observed in predicate
evaluations suddely exhibit a strong discontinuity, a kind of ``paper
retraction'' based on near-replications.  However, this requires
modifying the delta-debugging implementations, which is difficult and
sometimes not really feasible (e.g., few users of AFL-fuzz \cite{aflfuzz} will wish
to change its C code for test reduction).  Ideally, the solution
should be implementable simply by modifying the predictate that is
evaluated.

>>>>

In scientific literature, the most frequently proposed solution is the
use of replications:  repeated runs of ``successful'' experiments to
minimize the probability that a result is a fluke due to publication
bias.  One way to produce this effect would be to allow
delta-debugging to backtrack if the probabilties observed in predicate
evaluations suddely exhibit a strong discontinuity, a kind of ``paper
retraction'' based on near-replications.  However, this requires
modifying the delta-debugging implementations, which is difficult and
sometimes not really feasible (e.g., few users of afl-fuzz \cite{aflfuzz} will wish
to change its C code for test reduction).  Ideally, the solution
should be implementable simply by modifying the predictate that is
evaluated.
